---
title: "Drake: Billboard Records & Streaming Dominance"
---

Welcome to the Drake music analytics project. This site examines Drake's historic career through **thousands of data points**—combining **2,569 weekly Billboard Hot 100 observations** from [TidyTuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-09-14) with over **140 billion Spotify streams** from [kworb.net](https://kworb.net/spotify/artist/3TVXtAsR1Inumwj472S9r4_songs.html) and track telemetry from [Songstats](https://songstats.com/track/ul9j1yr4/drake).

::: {.stat-grid}
::: {.stat-card}
::: {.stat-number}
2,569
:::
::: {.stat-label}
Billboard Chart Observations
:::
:::

::: {.stat-card}
::: {.stat-number}
140.7B
:::
::: {.stat-label}
Total Spotify Streams
:::
:::

::: {.stat-card}
::: {.stat-number}
51
:::
::: {.stat-label}
Weeks at #1
:::
:::

::: {.stat-card}
::: {.stat-number}
547
:::
::: {.stat-label}
Spotify Charted Songs
:::
:::
:::

## Career Chart Trajectory (2,569 Observations)

The visualization below is constructed from **2,569 individual weekly chart appearances** by Drake on the Billboard Hot 100 between 2009 and 2021. Every point captures a single week on the chart, colored by whether Drake was the primary lead artist or a featured collaborator. The trend lines illustrate how Drake maintained an unbroken top-tier chart presence across more than a decade.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 5.6
#| dpi: 300

library(tidyverse)

drake_bb <- read_csv("data/drake_billboard.csv", show_col_types = FALSE) |> 
  mutate(
    role = if_else(str_starts(performer, "Drake"), "Lead Artist", "Featured Artist")
  )

ggplot(drake_bb, aes(x = week_date, y = week_position, color = role)) +
  geom_point(alpha = 0.45, size = 2.0) +
  geom_smooth(se = FALSE, method = "loess", span = 0.32, linewidth = 1.3) +
  scale_y_reverse(breaks = c(1, 10, 25, 50, 75, 100)) +
  scale_color_manual(values = c("Lead Artist" = "#6366f1", "Featured Artist" = "#f43f5e")) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(
    title = "Drake on the Billboard Hot 100 (2009–2021)",
    subtitle = "Tracking 2,569 weekly positions across lead singles & guest collaborations",
    x = "Year",
    y = "Billboard Hot 100 Rank (1 is top)",
    color = NULL,
    caption = "Source: TidyTuesday / Billboard.com Archive (2,569 observations)"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 16, color = "#0f172a"),
    plot.subtitle = element_text(color = "#64748b", margin = margin(b = 14)),
    legend.position = "top",
    legend.text = element_text(face = "bold", color = "#334155", size = 11),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "#f1f5f9"),
    plot.background = element_rect(fill = "#ffffff", color = "#e0e7ff", linewidth = 1.2),
    plot.margin = margin(16, 16, 16, 16)
  )
```

::: {style="display: flex; gap: 0.75rem; margin-bottom: 2rem;"}
<a href="explorer.html" class="btn btn-primary btn-sm">Explore Interactive Billboard Data &rarr;</a>
<a href="features.html" class="btn btn-outline-primary btn-sm">Read Story: The Feature Effect &rarr;</a>
:::

---

## Spotify Streaming Dominance

Alongside his historical Billboard dominance, Drake is one of the most-streamed artists in Spotify history, accumulating **over 140 billion streams**. 

Explore Drake's top 10 most-streamed hits. **Hover over any track below to instantly play an audio preview** (or click to play). Move your mouse away to pause.

```{r}
#| echo: false
#| message: false
#| warning: false
#| results: asis

library(tidyverse)
library(htmltools)

previews <- read_csv("data/top_song_previews.csv", show_col_types = FALSE)
max_streams <- max(previews$streams)

rows <- purrr::map(seq_len(nrow(previews)), function(i) {
  row <- previews[i, ]
  pct <- round((row$streams / max_streams) * 100, 1)
  streams_b <- paste0(round(row$streams / 1e9, 2), "B streams")
  role_class <- if (row$role == "Lead Artist") "lead" else "feature"
  badge_style <- if (row$role == "Lead Artist") {
    "background:#dbeafe; color:#1e40af; font-size:0.72rem; font-weight:600; padding:2px 8px; border-radius:9999px;"
  } else {
    "background:#ffedd5; color:#c2410c; font-size:0.72rem; font-weight:600; padding:2px 8px; border-radius:9999px;"
  }

  tags$div(
    class = "audio-chart-row",
    `data-audio` = row$preview_url,
    `data-title` = row$title,
    tags$div(class = "audio-chart-rank", paste0("#", row$rank)),
    tags$img(class = "audio-chart-art", src = row$artwork, alt = row$title),
    tags$div(
      class = "audio-bar-wrapper",
      tags$div(
        class = "audio-bar-title-row",
        tags$span(class = "audio-bar-title", row$title),
        tags$span(style = badge_style, row$role)
      ),
      tags$div(
        class = "audio-bar-track",
        tags$div(class = paste("audio-bar-fill", role_class), style = paste0("width: ", pct, "%;"))
      )
    ),
    tags$div(class = "audio-chart-stat", streams_b)
  )
})

script <- tags$script(HTML("
document.addEventListener('DOMContentLoaded', function() {
  const audio = new Audio();
  audio.preload = 'none';
  const nowPlayingEl = document.getElementById('now-playing-title-home');
  const waveEl = document.getElementById('audio-wave-home');
  const rows = document.querySelectorAll('.audio-chart-container-home .audio-chart-row');
  let currentSrc = '';

  function playTrack(row) {
    const src = row.getAttribute('data-audio');
    const title = row.getAttribute('data-title');
    if (!src) return;
    rows.forEach(r => r.classList.remove('is-playing'));
    row.classList.add('is-playing');
    if (currentSrc !== src) {
      audio.src = src;
      currentSrc = src;
    }
    audio.play().then(() => {
      if (nowPlayingEl) nowPlayingEl.textContent = 'Playing: ' + title;
      if (waveEl) waveEl.style.display = 'inline-flex';
    }).catch(() => {
      if (nowPlayingEl) nowPlayingEl.textContent = 'Click to enable audio (' + title + ')';
    });
  }

  function stopTrack() {
    audio.pause();
    rows.forEach(r => r.classList.remove('is-playing'));
    if (nowPlayingEl) nowPlayingEl.textContent = 'Hover over a track to play';
    if (waveEl) waveEl.style.display = 'none';
  }

  rows.forEach(row => {
    row.addEventListener('mouseenter', () => playTrack(row));
    row.addEventListener('mouseleave', stopTrack);
    row.addEventListener('click', () => playTrack(row));
  });
});
"))

chart_widget <- tags$div(
  class = "audio-chart-container audio-chart-container-home",
  tags$div(
    class = "audio-chart-header",
    tags$div(
      class = "audio-chart-prompt",
      tags$span(style = "font-size: 1.25rem;", "🎧"),
      tags$strong("Interactive Audio Jukebox:"),
      tags$span("Hover over any bar below to hear an instant preview")
    ),
    tags$div(
      class = "audio-now-playing",
      tags$div(id = "audio-wave-home", class = "sound-wave", style = "display: none;",
        tags$span(), tags$span(), tags$span(), tags$span()
      ),
      tags$span(id = "now-playing-title-home", "Hover over a track to play")
    )
  ),
  tags$div(class = "audio-chart-list", rows),
  script
)

cat(as.character(chart_widget))
```

[Browse Full 500-Song Spotify Catalog &rarr;](spotify.html){.btn .btn-outline-primary .btn-sm}

---

## Featured Cross-Platform Track

Track-level telemetry from [Songstats](https://songstats.com/track/ul9j1yr4/drake) illustrates global DSP footprint:

::: {.track-card}
<img src="https://i.scdn.co/image/ab67616d00001e02f0c843a56521f2be4d0d10e2" alt="Drake Track Artwork" class="track-art" />

<div>
  <h4 style="margin-top:0;">Track: "Drake"</h4>
  <p style="margin-bottom:0.4rem; color:#475569;"><strong>Artists:</strong> Alsago & Slight Shady &bull; <strong>Release Date:</strong> March 13, 2026</p>
  <p style="margin-bottom:0.4rem; color:#475569;"><strong>ISRC:</strong> <code>CAHQJ2683690</code> &bull; <strong>Distribution:</strong> 184 Countries across Spotify, Apple Music, Deezer, Amazon & Tidal</p>
  <p style="margin-bottom:0;"><a href="songstats.html" class="btn btn-outline-primary btn-sm">View Songstats Track &rarr;</a> <a href="https://songstats.com/track/ul9j1yr4/drake" target="_blank" class="btn btn-outline-secondary btn-sm">Open on Songstats.com &nearr;</a></p>
</div>
:::
