---
title: "Spotify Streaming Analytics"
---

This section analyzes Drake's global streaming footprint on Spotify based on catalog data tracked by [kworb.net](https://kworb.net/spotify/artist/3TVXtAsR1Inumwj472S9r4_songs.html). Drake is one of the most-streamed artists in Spotify history, having amassed over **140 billion streams** across 547 charted songs.

::: {.stat-grid}
::: {.stat-card}
::: {.stat-number}
140.7B
:::
::: {.stat-label}
Total Spotify Streams
:::
:::

::: {.stat-card}
::: {.stat-number}
65.9M
:::
::: {.stat-label}
Daily Streams
:::
:::

::: {.stat-card}
::: {.stat-number}
547
:::
::: {.stat-label}
Catalog Tracks
:::
:::

::: {.stat-card}
::: {.stat-number}
4.48B
:::
::: {.stat-label}
#1 Song (One Dance)
:::
:::
:::

## Catalog Stream Distribution

Drake's catalog spans solo releases, lead tracks with guest artists, and guest features on other artists' tracks. The data demonstrates how guest features played a massive role in building his cumulative streaming audience.

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(knitr)

summary_data <- read_csv("data/kworb_summary.csv", show_col_types = FALSE)

summary_data |> 
  kable(
    col.names = c("Metric", "Total", "As Lead", "Solo", "As Feature (*)"),
    align = c("l", "r", "r", "r", "r")
  )
```

## Interactive Audio Jukebox: Top 10 Most-Streamed Songs

Explore Drake's top 10 all-time streaming records. **Hover over any track below to instantly play an audio preview** (or tap/click on mobile). Move your cursor away to pause playback.

```{r}
#| echo: false
#| message: false
#| warning: false
#| results: asis

library(tidyverse)
library(scales)
library(htmltools)

previews <- read_csv("data/top_song_previews.csv", show_col_types = FALSE)
songs_data <- read_csv("data/kworb_songs.csv", show_col_types = FALSE)
max_streams <- max(previews$streams)

rows <- purrr::map(seq_len(nrow(previews)), function(i) {
  row <- previews[i, ]
  pct <- round((row$streams / max_streams) * 100, 1)
  streams_b <- paste0(round(row$streams / 1e9, 2), "B streams")
  role_class <- if (row$role == "Lead Artist") "lead" else "feature"
  badge_style <- if (row$role == "Lead Artist") {
    "background:#dbeafe; color:#1e40af; font-size:0.72rem; font-weight:600; padding:2px 8px; border-radius:9999px;"
  } else {
    "background:#ffedd5; color:#c2410c; font-size:0.72rem; font-weight:600; padding:2px 8px; border-radius:9999px;"
  }

  tags$div(
    class = "audio-chart-row",
    `data-audio` = row$preview_url,
    `data-title` = row$title,
    tags$div(class = "audio-chart-rank", paste0("#", row$rank)),
    tags$img(class = "audio-chart-art", src = row$artwork, alt = row$title),
    tags$div(
      class = "audio-bar-wrapper",
      tags$div(
        class = "audio-bar-title-row",
        tags$span(class = "audio-bar-title", row$title),
        tags$span(style = badge_style, row$role)
      ),
      tags$div(
        class = "audio-bar-track",
        tags$div(class = paste("audio-bar-fill", role_class), style = paste0("width: ", pct, "%;"))
      )
    ),
    tags$div(class = "audio-chart-stat", streams_b)
  )
})

script <- tags$script(HTML("
document.addEventListener('DOMContentLoaded', function() {
  const audio = new Audio();
  audio.preload = 'none';
  const nowPlayingEl = document.getElementById('now-playing-title');
  const waveEl = document.getElementById('audio-wave');
  const rows = document.querySelectorAll('.audio-chart-row');
  let currentSrc = '';

  function playTrack(row) {
    const src = row.getAttribute('data-audio');
    const title = row.getAttribute('data-title');
    if (!src) return;
    rows.forEach(r => r.classList.remove('is-playing'));
    row.classList.add('is-playing');
    if (currentSrc !== src) {
      audio.src = src;
      currentSrc = src;
    }
    audio.play().then(() => {
      if (nowPlayingEl) nowPlayingEl.textContent = 'Playing: ' + title;
      if (waveEl) waveEl.style.display = 'inline-flex';
    }).catch(() => {
      if (nowPlayingEl) nowPlayingEl.textContent = 'Click to enable audio (' + title + ')';
    });
  }

  function stopTrack() {
    audio.pause();
    rows.forEach(r => r.classList.remove('is-playing'));
    if (nowPlayingEl) nowPlayingEl.textContent = 'Hover over a track to play';
    if (waveEl) waveEl.style.display = 'none';
  }

  rows.forEach(row => {
    row.addEventListener('mouseenter', () => playTrack(row));
    row.addEventListener('mouseleave', stopTrack);
    row.addEventListener('click', () => playTrack(row));
  });
});
"))

chart_widget <- tags$div(
  class = "audio-chart-container",
  tags$div(
    class = "audio-chart-header",
    tags$div(
      class = "audio-chart-prompt",
      tags$span(style = "font-size: 1.25rem;", "🎧"),
      tags$strong("Interactive Audio Jukebox:"),
      tags$span("Hover over any bar below to hear an instant preview")
    ),
    tags$div(
      class = "audio-now-playing",
      tags$div(id = "audio-wave", class = "sound-wave", style = "display: none;",
        tags$span(), tags$span(), tags$span(), tags$span()
      ),
      tags$span(id = "now-playing-title", "Hover over a track to play")
    )
  ),
  tags$div(class = "audio-chart-list", rows),
  script
)

cat(as.character(chart_widget))
```


## Top 10 Daily Stream Velocity

Streaming velocity indicates songs that continue to experience high daily playback today.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9.5
#| fig-height: 5
#| dpi: 300

top_daily <- songs_data |> 
  arrange(desc(daily)) |> 
  slice_head(n = 10) |> 
  mutate(title = fct_reorder(title, daily))

ggplot(top_daily, aes(x = daily / 1e6, y = title, fill = role)) +
  geom_col(width = 0.68, color = "#ffffff", linewidth = 0.6) +
  geom_text(
    aes(label = str_c(round(daily / 1e6, 2), "M/day")),
    hjust = -0.12,
    size = 3.6,
    fontface = "bold",
    color = "#1e293b"
  ) +
  scale_x_continuous(
    labels = label_number(suffix = "M"),
    expand = expansion(mult = c(0, 0.22))
  ) +
  scale_fill_manual(values = c("Lead Artist" = "#6366f1", "Featured Artist" = "#f43f5e")) +
  labs(
    title = "Top 10 Drake Tracks by Daily Spotify Streams",
    subtitle = "Current streaming velocity in millions of plays per day",
    x = "Daily Streams (Millions)",
    y = NULL,
    fill = NULL,
    caption = "Source: kworb.net Spotify Artist Songs Tracker"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 15, color = "#0f172a"),
    plot.subtitle = element_text(color = "#64748b", margin = margin(b = 10)),
    legend.position = "top",
    legend.text = element_text(face = "bold", color = "#334155", size = 11),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "#f1f5f9"),
    plot.background = element_rect(fill = "#ffffff", color = "#e0e7ff", linewidth = 1.2),
    plot.margin = margin(16, 16, 16, 16)
  )
```

## Complete Spotify Songs Catalog (Top 500)

Use the table below to search and sort Drake's top 500 songs on Spotify by total streams, daily streams, or role.

```{r}
#| echo: false
#| message: false
#| warning: false

library(DT)

display_table <- songs_data |> 
  select(
    Rank = rank,
    `Song Title` = title,
    `Role` = role,
    `All-Time Streams` = streams,
    `Daily Streams` = daily
  )

datatable(
  display_table,
  filter = "top",
  rownames = FALSE,
  class = "hover stripe compact",
  options = list(
    pageLength = 20,
    lengthMenu = c(10, 20, 50, 100),
    autoWidth = TRUE,
    scrollX = TRUE
  )
) |> 
  formatCurrency(
    columns = c("All-Time Streams", "Daily Streams"),
    currency = "",
    digits = 0
  )
```
